---
title: 'Lab 2: Chocalate Testing'
author: "Christopher Spartz"
date: "9/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
## #1
```{r}
library(classdata)
library(ggplot2)
Cocoa <-choco$CocoaPercent
hist(Cocoa, main = "Frequency  of ratings per Cocoa Percent", xlab = "Cocoa Percent")
boxplot(Cocoa, ylab = "Cocoa Percent", xlab = "Frequency", main = "Frequency  of ratings per Cocoa Percent")
#boxplot.stats(choco$CocoaPercent)$out
```


## #2
```{r}
country <- table(choco$CountryBeanOrigin)
country <- country[country > 10]
barplot(country, main="Number of Ratings of Beans by Country Origin",xlab="Country of Origin",ylab="Number of ratings", las=2, cex.names=.5)
```


## #3
```{r}
rcp <- choco$Rating/choco$CocoaPercent
hist(rcp, main = "Ratings/CocoaPercent", xlab = "Ratings/CocoaPercent")
summary(rcp)
```
Ratings of chocolate tends to go up as Cocoa Percent increases, until it hits a point where the Cocoa percent is too high, and the rating falls with a high cocoa percent. This histogram shows that relation by showing the frequency with which a higher rating is given to high cocoa percents.

## #4
```{r}
cr <- table(choco$CountryBeanOrigin,choco$Rating)
cr
barplot(cr)
```



## #5
The first of my 2 analyses: How does the number of ratings depend on company making the chocolate? Another way of putting that, what are the biggest chocolate companies?
```{r}
company <- table(choco$Company)
company <- company[company > 10]
median(company)
quantile(company)
min(company)
max(company)
barplot(company, main="Number of Ratings of Beans by Company",xlab="Company",ylab="Number of ratings", las=2, cex.names=.5)
```
For the largest companies
